### 2013-07-07 mcmc.tex
notes to self

Despite all this, in many cases,
  data analysts believe they are sampling the likelihood.
This is because (we presume) they have put a likeilihood function
  (or log-likelihood function)
  in as the input to the MCMC code, where the probability function
  (or log-probability function) should go.
Then is it the likelihood that is being sampled?
No, not really;
it is a posterior probability that is directly proportional to the likelihood function.
That is, it is a posterior probability for some implicit (and improper) ``flat'' priors.

@@

@@

>>>>

Despite all this, in many cases,
  data analysts believe they are sampling the likelihood.
This is because (we presume) they have put a likelihood function
  (or log-likelihood function)
  in as the input to the MCMC code, where the probability function
  (or log-probability function) should go.
Then is it the likelihood that is being sampled?
No, not really;
it is a posterior probability that is directly proportional to the likelihood function.
That is, it is a posterior probability for some implicit (and improper) ``flat'' priors.

@@

...Simple problems where the outputs are analytic.  Functional testing.

@@

...Sample the prior (likelihood set to unity) to check priors and parameterization (another functional test).
